Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-10-14 summary.Rmd
more simulations

## Case $K = 2$

@@

* Number of underlying communities $K = 2$
* Mixture parameter $\alpha = .5$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

### Community detection

In this part, we will assess Algorithm 2's performance for sample sizes 
$n = 64, 128, 256, 512, 1024, 2048$. For each sample size $n$, $100$ sets of 
$\lambda^{(kl)}$'s are drawn and for each set of parameters, one adjacency 
matrix $A$ is drawn and clustered. We will not consider community detection using the 
edge probability matrix $P$ since this will always result exact recovery of the
original communities (up to permutation).

```{r clust_err_sim, fig.cap = 'IQR clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = 'misclustering proportion', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1')
```

@@

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE}
clustering.df <- readr::read_csv('clustering.csv')
clustering.df %>%
  dplyr::group_by(n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = 'misclustering count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1')
```

We can also examine how the distribution of $(\hat{v}_i)^\top \hat{v_j}$ varies 
with $n$:

```{r, fig.cap = 'Between-cluster inner products of the eigenvectors of $A$ for varying sample sizes.', cache = FALSE}
densities.df <- readr::read_csv('densities.csv')

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods * n, colour = factor(n))) + 
  labs(x = expression(n * v[i]^T * v[j]),
       colour = 'n') + 
  scale_colour_brewer(palette = 'Set1')
```

### Parameter estimation

Figure \ref{fig:lambda_est} shows the medians and interquartile ranges of root 
mean square errors for Algorithm 4 over 100 simulations using the same 
parameters as before. Comparison against an MLE-based method 
\cite{noroozi2019estimation} suggests similar performance, close to the rate 
$n^{-1/2}$.

```{r lambda_est, cache = FALSE, fig.cap = 'Log-log plot of the median and IQR RMSE from Algorithm 4 (red) compared against an MLE-based method (blue) using sample sizes from 64 to 2048. Simulations were repeated 100 times for each sample size.'}
rmse.df <- readr::read_csv('rmse.csv')

rmse.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75),
                   median.rmse.mle = median(rmse.mle),
                   q1.rmse.mle = quantile(rmse.mle, .25),
                   q3.rmse.mle = quantile(rmse.mle, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() +
  geom_line(aes(x = n, y = median.rmse, colour = 'Algorithm 4')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse,
                    colour = 'Algorithm 4')) + 
  geom_line(aes(x = n, y = median.rmse.mle, colour = 'MLE-based')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse.mle, ymax = q3.rmse.mle,
                   colour = 'MLE-based')) + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(y = 'RMSE', colour = NULL)
```

## Higher values of $K$

* Number of underlying communities $K = 2, 4, 8$
* Mixture parameters $\alpha_k = 1 / K$ for $k = 1, ..., K$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

### Community detection

```{r clust_err_k, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 8}
clustering.df <- readr::read_csv('clustering-k.csv')
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  scale_y_log10() +
  # scale_x_log10() + 
  labs(y = '1 - adjusted rand index', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both')
```

### Parameter estimation

```{r lambda_est_k, cache = FALSE, fig.cap = 'Log-log plot of the median and IQR RMSE from Algorithm 4 (red) compared against an MLE-based method (blue) using sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 100 times for each sample size.', fig.width = 8}
rmse.df <- readr::read_csv('rmse.csv') %>% 
  dplyr::transmute(K = 2,
                   n = n,
                   rmse = rmse,
                   rmse.mle = rmse.mle) %>% 
  dplyr::bind_rows(readr::read_csv('rmse-k.csv'))

rmse.df %>% 
  na.omit() %>% 
  dplyr::group_by(K, n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75),
                   median.rmse.mle = median(rmse.mle),
                   q1.rmse.mle = quantile(rmse.mle, .25),
                   q3.rmse.mle = quantile(rmse.mle, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() + 
  scale_y_log10() + 
  scale_x_log10() +
  geom_line(aes(x = n, y = median.rmse, colour = 'Algorithm 4')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse,
                    colour = 'Algorithm 4')) + 
  geom_line(aes(x = n, y = median.rmse.mle, colour = 'MLE-based')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse.mle, ymax = q3.rmse.mle,
                   colour = 'MLE-based')) + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(y = 'RMSE', colour = NULL) + 
  facet_wrap(~ K, labeller = 'label_both')
```

@@

In the third example,

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2.', fig.height = 2}
hh <- readRDS('data/village-hh-59.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 6
zhat.hh <- cluster.pabm(A.hh, K, 
                        use.all = TRUE, normalize = FALSE, p = K, q = 0)

zhat.mres <- readRDS('data/mres-result.rds')

gridExtra::grid.arrange(plot.A(A.hh, zhat.hh), 
                        plot.A(A.hh, zhat.mres),
                        ncol = 2)
```

>>>>

## Balanced communities

In each simulation, community labels $z_1, ..., z_n$ were drawn 
from a multinomial distribution with mixture parameters 
$\{\alpha_1, ..., \alpha_K\}$, then $\{\lambda^{(kl)}\}_K$ according to the 
drawn community labels, $P$ was constructed using the drawn 
$\{\lambda^{(kl)}\}_K$, and $A$ was drawn from $P$ by 
$A_{ij} \stackrel{indep}{\sim} Bernoulli(P_{ij})$. Each simulation has a unique
edge probability matrix $P$.

@@

* Number of vertices $n = 256, 512, 1024, 2048, 4096$
* Number of underlying communities $K = 2, 3, 4$
* Mixture parameters $\alpha_k = 1 / K$ for $k = 1, ..., K$, (i.e., each 
community has an equal probability of being drawn)
* Community labels 
$z_k \stackrel{iid}{\sim} Multinomial(\alpha_K, ..., \alpha_K)$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

$50$ simulations were performed for each $(n, K)$ pair.

```{r clust_err_k, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 50 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
# mod.max.df <- readr::read_csv('mod-max-k.csv') %>% 
#   dplyr::group_by(K, n) %>% 
#   dplyr::summarise(med.err.mm = median(error.mm),
#                    first.q.mm = quantile(error.mm, .25),
#                    third.q.mm = quantile(error.mm, .75)) %>% 
#   dplyr::ungroup()
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  # scale_x_log10() + 
  labs(y = 'community detection error', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  # geom_line(data = mod.max.df,
  #           aes(x = n, y = med.err.mm,
  #               colour = 'modularity maximization')) + 
  # geom_errorbar(data = mod.max.df,
  #               aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
  #                   colour = 'modularity maximization')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_x_continuous(breaks = c(256, 512, 1024, 2048, 4096)) +
  scale_y_log10()
```

@@

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048. Simulations were repeated 100 times for each sample size. The $y$-axis is shown on a logarithmic scale.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  # scale_x_log10() + 
  labs(y = 'misclustering count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10() +
  scale_x_continuous(breaks = c(256, 512, 1024, 2048, 4096))
```

```{r lambda_est_k, cache = FALSE, fig.cap = 'Log-log plot of the median and IQR RMSE from Algorithm 4 (red) compared against an MLE-based method (blue) using sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 50 times for each sample size.', fig.width = 10}
rmse.df <- readr::read_csv('rmse.csv') %>% 
  dplyr::transmute(K = 2,
                   n = n,
                   rmse = rmse,
                   rmse.mle = rmse.mle) %>% 
  dplyr::bind_rows(readr::read_csv('rmse-k.csv'))

rmse.df %>% 
  na.omit() %>% 
  dplyr::group_by(K, n) %>% 
  dplyr::summarise(median.rmse = median(rmse),
                   q1.rmse = quantile(rmse, .25),
                   q3.rmse = quantile(rmse, .75),
                   median.rmse.mle = median(rmse.mle),
                   q1.rmse.mle = quantile(rmse.mle, .25),
                   q3.rmse.mle = quantile(rmse.mle, .75)) %>% 
  dplyr::ungroup() %>% 
  ggplot() +
  geom_line(aes(x = n, y = median.rmse, colour = 'Algorithm 4')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse, ymax = q3.rmse,
                    colour = 'Algorithm 4')) + 
  geom_line(aes(x = n, y = median.rmse.mle, colour = 'MLE-based')) + 
  geom_errorbar(aes(x = n, ymin = q1.rmse.mle, ymax = q3.rmse.mle,
                   colour = 'MLE-based')) + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(y = 'RMSE', colour = NULL) + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10() + 
  scale_x_log10(breaks = c(64, 128, 256, 512, 1024, 2048))
```

## Imbalanced communities

Simulations performed in this section are similar to those in the previous 
section with the exception of the mixture parameters 
$\{\alpha_1, ..., \alpha_K\}$ used to draw community labels from the 
multinomial distribution. For these examples, we set the following parameters:

* Number of vertices $n = 256, 512, 1024, 2048, 4096$
* Number of underlying communities $K = 2, 3, 4$
* Mixture parameters $\alpha_k = \frac{k^{-1}}{\sum_{l=1}^K l^{-1}}$ for 
$k = 1, ..., K$
* Community labels 
$z_k \stackrel{iid}{\sim} Multinomial(\alpha_K, ..., \alpha_K)$
* Within-group popularities $\lambda^{(kk)} \stackrel{iid}{\sim} Beta(2, 1)$
* Between-group popularities 
$\lambda^{(kl)} \stackrel{iid}{\sim} Beta(1, 2)$ for $k \neq l$

$50$ simulations were performed for each $(n, K)$ pair.

```{r clust_err_k_imba, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against subspace clustering (blue) for sample sizes from 64 to 2048 and number of clusters from 2 to 8. Simulations were repeated 50 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k-imbalanced.csv')
clustering.df %>%
  dplyr::group_by(K, n) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  # scale_x_log10() + 
  labs(y = 'community detection error', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'Algorithm 2')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'Algorithm 2')) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC')) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_x_continuous(breaks = c(256, 512, 1024, 2048, 4096)) +
  scale_y_log10()
```

## Replication and comparison of simulations from \citet*{307cbeb9b1be48299388437423d94bf1}

```{r clust_err_sc, fig.cap = 'IQR of clustering error using Algorithm 2 (red) compared against modularity maximization (blue) for sample size equal to 400. Simulations were repeated 50 times for each sample size. The $y$-axis is shown on a logarithmic scale.', fig.height = 2, fig.width = 6}
clustering.mm.df <- readr::read_csv('clustering-sim-sc.csv')
clustering.ase.df <- readr::read_csv('clustering-sim-sc-ase.csv')
clustering.df <- dplyr::bind_rows(
  clustering.mm.df %>% 
    dplyr::transmute(method = 'Modularity maximization',
                     homophily = homophily,
                     error = pa.err),
  clustering.ase.df %>% 
    dplyr::transmute(method = 'Algorithm 2',
                     homophily = homophily,
                     error = pa.err)
)
clustering.df %>%
  dplyr::group_by(method, homophily) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75)) %>%
  dplyr::ungroup() %>% 
  ggplot() +
  labs(y = 'community detection \nerror', 
       colour = NULL) +
  geom_line(aes(x = homophily, y = med.err, colour = method)) +
  geom_errorbar(aes(x = homophily, ymin = first.q, ymax = third.q,
                    colour = method)) + 
  scale_colour_brewer(palette = 'Set1') + 
  # coord_fixed(1) + 
  scale_y_log10()
```

## Additional experiments

Using the same set of parameters for generating $P$ and $A$ as in the 
balanced communities examples for $K = 2$, we generated one instance of $A$ for
each $n$ and constructed $B$ according to algorithm 4 to verify that 
as $n \to \infty$, $(\hat{v}_i)^\top \hat{v_j} \stackrel{P}{\to} 0$ for $i, j$ 
in different clusters. Furthermore, the distribution of these inner products 
should be approximately normal.

```{r, fig.cap = 'Between-cluster inner products of the eigenvectors of $A$ for varying sample sizes.', fig.height = 2, fig.width = 4}
densities.df <- readr::read_csv('densities.csv')

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods * n, colour = factor(n))) + 
  labs(x = expression(n * v[i]^T * v[j]),
       colour = 'n') + 
  scale_x_continuous(breaks = seq(-5, 5)) + 
  scale_colour_brewer(palette = 'Set1')
```

@@

In the third example, we consider the Karantaka villages data studied by 
\citet{DVN/U3BIHX_2013}. For this example, we chose the `visitgo` network from 
village 12 at the household level. The label of interest is the religious 
affiliation. The network was truncated to religions "1" and "2", and vertices 
of degree 0 were removed. The resulting network has 141 vertices.

```{r, cache = FALSE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2 (left), sparse subspace clustering (middle), and modularity maximization (right).', fig.height = 2, fig.width = 8, eval = TRUE}
hh <- readRDS('data/village-hh-12.rds')
A.hh <- hh$A
z.hh <- hh$z
K <- 2
zhat.hh <- cluster.pabm(A.hh, K,
                        use.all = TRUE, normalize = FALSE, p = 3, q = 1)
zhat.hh.ssc <- ssc(A.hh, K, lambda = .1)

# this part of code taken from sengupta & chen
setwd('~/dev/pabm-grdpg/codes_and_data')
require(MASS);require("clue")
source("EPalgosim.R") 
source("functions.R")
b.can = EPalgo(A.hh,eps=0) # EP algorithm (no perturbation)
Q.PA.can = rep(NA, ncol(b.can))	# array to store Q values
for (i in 1:ncol(b.can)){
  #check if any cluster is empty
  foo = rep(NA, max(z.hh))
  for (clus in 1:max(z.hh)) {foo[clus]=sum(b.can[,i]==clus)}
  if (min(foo)==0) {stop('Empty groups are not allowed')} 
  Q.PA.can[i] = Q.PA(A.hh, b=b.can[,i])   # fit PABM
} # end of i for loop
foo1 = order(-Q.PA.can)[1] 
zhat.hh.mm = b.can[,foo1]   # community assignment that maximises Q.PA

gridExtra::grid.arrange(plot.A(A.hh, zhat.hh),
                        plot.A(A.hh, zhat.hh.ssc),
                        plot.A(A.hh, zhat.hh.mm),
                        nrow = 1)
```

```{r, eval = TRUE}
hh.acc <- mean(zhat.hh == z.hh)
hh.acc <- ifelse(hh.acc < .5, 1 - hh.acc, hh.acc)
hh.acc.ssc <- mean(zhat.hh.ssc == z.hh)
hh.acc.ssc <- ifelse(hh.acc.ssc < .5, 1 - hh.acc.ssc, hh.acc.ssc)
hh.acc.mm <- mean(zhat.hh.mm == z.hh)
hh.acc.mm <- ifelse(hh.acc.mm < .5, 1 - hh.acc.mm, hh.acc.mm)

knitr::kable(data.frame(method = c('Algorithm 2', 'SSC', 
                                   'Modularity maximization'),
                        error = round(1 - c(hh.acc, hh.acc.ssc, hh.acc.mm), 3)),
             caption = paste('Community detection error rates for identifying',
                             'household religion.'))
```
